### 2017-03-03 paper/oopsla17-submission/related.tex
sketch outline of paper

Given a defect, fault localization is the task of identifying
``suspicious'' program elements (e.g., lines, statements) that are likely
implicated in the defect (i.e., that should be changed to fix the defect). 
Perhaps the best-known is Tarantula, which uses a simple mathematical
formula based on measured information from dynamic normal and buggy
runs~\cite{FIXME}. Other similar approaches, including those of
Jacquard~\cite{FIXME} and Ochiai~\cite{FIXME} consider alternate features
of information or refined formulae and generally obtain more precise
results; see Wong for a survey~\cite{FIXME}. While some researchers have
approached such fault localization with an eye toward optimality (e.g.,
Harman et al. determine optimal coefficients~\cite{FIXME}), in general
such fault localization approaches are limited by their reliance on either
running tests or including relevant features. For example, Tarantula-based 
techniques require a normal and a buggy run of the program. By contrast,
we consider incomplete programs with type errors that may not be executed
in any standard sense. Similarly, the features available influence the
classes of defects that can be localized. A fault localization scheme based
purely on control flow features lines will have difficulty with cross-site
scripting or SQL code injection attacks, which follow the same control flow
path on normal and buggy runs (differing only in the user-supplied data).
By contrast, we FIXME-ERIC.

>>>>

Given a defect, fault localization is the task of identifying
``suspicious'' program elements (e.g., lines, statements) that are likely
implicated in the defect (i.e., that should be changed to fix the defect). 
Perhaps the best-known is Tarantula, which uses a simple mathematical
formula based on measured information from dynamic normal and buggy
runs~\cite{Jones2002-us}. Other similar approaches, including those of
Jaccard~\cite{Chen2002-qz} and
Ochiai~\cite{Abreu2006-fn,Abreu2007-mu} consider alternate features
of information or refined formulae and generally obtain more precise
results; see Wong for a survey~\cite{Wong2009-pd}. While some researchers have
approached such fault localization with an eye toward optimality (e.g.,
Harman et al. determine optimal coefficients~\cite{Yoo2013-rw}), in general
such fault localization approaches are limited by their reliance on either
running tests or including relevant features. For example, Tarantula-based 
techniques require a normal and a buggy run of the program. By contrast,
we consider incomplete programs with type errors that may not be executed
in any standard sense. Similarly, the features available influence the
classes of defects that can be localized. A fault localization scheme based
purely on control flow features lines will have difficulty with cross-site
scripting or SQL code injection attacks, which follow the same control flow
path on normal and buggy runs (differing only in the user-supplied data).
By contrast, we FIXME-ERIC.
